---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# reportGenerator

<!-- badges: start -->
<!-- badges: end -->

Automatic report generator of the Darwin EU studies. 

## Installation

You can install the development version of reportGenerator like so:

``` r
install.packages("remotes")
remotes::install_github("cbarbozaerasmus/reportGenerator")
```

## Example

The function reportIncidencePrevalence takes a character string for title and author. Then a tibble for incidence and prevalence from IncidencePrevalence package. 

```{r }
library(reportGenerator)
library(IncidencePrevalence)

title <- "..."
author <- "..."
prevalence <- prevalence$prevalence_estimates
incidence <- incidence$incidence_estimates

## RUN

reportIncidencePrevalence(title,
                          author,
                          prevalence,
                          incidence)
```

It generates an HTML document in the reports folder. 
